Analytics Without Parameter Tuning Considered Harmful?

### 2015-03-15 tuningpredictor.tex
Updates from ShareLaTeX

\input{algo}
The psuedocode for differential evolution is shown in Algorithm~\ref{alg:DE}.
Note that, as we describe the algorithm,
  any superscript number denotes a line in that algorithm.

@@

The premise of this algorithm is that the best way to mutate existing tunings
is to {\em Extrapolate}$^{29}$
between current solutions.  Three solutions $a,b,c$ are selected at random.
For each tuning parameter $i$, at some probability {\em cr}, we replace  new tuning is created
via:
\bi
\item For numerics: $a_i+f \times (b_i - c_i)$   where $f$ is a parameter
controlling the cross-over amount.  The {\em trim} function$^{39}$ limits the new
value to the legal range min..max of that parameter.
\item For booleans:  negate the current value$^{37}$.
\ei
The main loop of DE$^7$ runs over the {\em Population}, replacing old items
with new {\em Candidate}s (if the new candidate is better than the old item).
This means that, as the loop progresses, the {\em Population} is full of increasiningly
more valuable solutions. This, in turn, also improves  the candidates (which are generated
from the {\em Population}.

@@

\section{Experiments}

The following experiments compare the performance of three learners, tuned and untuned, on 17
sets of data.

@@

An important principle in data mining is not to test on the data used
in training.  There are many ways to design a experiment that satisfies this principle:
\bi
\item  Leave-one-out experiments can be impractically slow for large data sets;
\item Cross-validation can mix up older and newer data sets so it may well be that
data from the {\em future} is used to train on {\em past data}.
\ei
To avoid these problems, we used an incremental learning approach. The following
experiment ensures that the training data was created at some time before the test
data.

For this experiment, we looked for data sets that had at least three  
releases in PROMISE:
\bi 
\item The {\em first} release was used for some  {\em training}, to collect a baseline
   using an untuned learner.
   \item
   The {\em first} release was also used  on line 24 of Algorithm~\ref{alg:DE} to
   build some model using some the tunings found in some {\em Candidate}.
   \item The {\em second} release was used on 25 of Algorithm~\ref{alg:DE} to 
   test the model found on line 24.
   \item Finally the {\em third} release was used to gather the performance statistics
   reported below from (a)~the model generated by the untuned learner or (b)~the
   best model found by differential evolution.

   \ei
 Note that the above ensures that all treatments get tested on the same final data set.

 Some data sets have more than three releases and, for those data, we could run more
 than one experiment. For example, {\em ant} has five versions in PROMISE so
 we ran three experiments called V0,V1,V2:
 \bi
 \item AntV0: first,second,third = versions 1,2,3
 \item AntV1: first,second,third = versions 2,3,4
 \item AntV2: first,second,third = versions 3,4,5
 \ei 
These data sets are displayed in \fig{data1} and \fig{data2}.

\subsection{Performance Scores}

To evaluate accuracy performance of learners, several measurements are used.
The 
probability of  detection({\it pd}) and probability of false alarm ({\it pf})\cite{menzies2007data}, 
the area under the receiver operating characteristics curve ({\it AUC})
\cite{lessmann2008benchmarking}, precision and F measure\cite{zhang2007comments}. In this work, we 
expect learners should identify as many defective modules as possible while avoiding false 
alarm. Therefore, learners are evaluated by both of {\it pd} and {\it pf} simaltanieously. A single 
measure, G-measure, defined as the harmonic mean of {\it pd} and $1-{\it pf}$  is used. The 
G-measure value is between 0 and 1. The higher, the better.
\begin{equation}
G = \frac{2*(1-pf)*pd}{1-pf+pd}
\end{equation}

In this experiment, we divide one project data set into training, tuning 
and testing datasets. In contrast to hold out way used in \cite{lessmann2008benchmarking, 
menzies2007data}, we separate the data sets in order. Since learners are designed to predict 
defects in future projects,  any randomly data set selection without taking into the time series 
will not sufficient to evaluate the performance of predicting future. Since we have data from 
10 different projects, each of which contains at least 3 evolutionary versions. We use the following policy 
to select the data for experiments: for each project, we use every three chronological data files 
to do testing, tuning and training in one experiment. For example, in ant project,
we have versions of $ant1.3$, $1.4$, $1.5$, $1.6$, and $1.7$, which will generate data sets called
 $antV0$, $antV1$ and $antV2$ for three experiments.

To investigates the impacts of parameters on learners, we use DE as the tuner and compare the G-measure 
values of Where-based learner with and without tuning, CART with and without tuning and Random 
Forests. Since the tuning time for Random Forests is very long, hopefully other researchers design
new heuristics to speed up the tuning process for Random Forests.  For the time being, even though
we don't tune Random Forests, if tuning help CART outperform Random Forests or improve itself performance ,
we still could conclude that tuning is helpful and necessary when comparing learners.

Besides the Where-based learner implemented by ourselves,  we use the CART and Random Forest modules 
from scikit-learn \cite{scikit-learn} to do a comparative study. The parameters associated with different learners are listed in Fig.\ref{fig:parameters}. For each data set, run CART, naive Where-based learner and Random Forests with corresponding default values. Then using DE to tune corresponding parameters for CART and Where-based Learner,  and run them again with the optimal parameters from tuning process to test the performance. 
% This study ranks learners using the Scott-Knott procedure recommended by Mittas \& Angelis in their 2013
% IEEE TSE paper~\cite{mittas2013ranking}.  This method sorts a list of $l$ treatments with $ls$ measurements by their median score. It then splits $l$ into sub-lists $m,n$ in order to maximize the expected value of differences  in the observed performances before and after divisions.

\section{Result}

@@

%%%%%%%%%%%%%%%% list of parameters%%%%%%%%%%%%%%%%%%%%%
\renewcommand\arraystretch{1.2}
\begin{figure*}[t!]
\renewcommand{\baselinestretch}{0.8}
\scriptsize
  \centering
\begin{tabular}{|c|c|c|c|l|}
\cline{1-5}
\begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular} & Parameters & Default &\begin{tabular}[c]{@{}c@{}}Tuning\\ Range\end{tabular}& 
\multicolumn{1}{c|}{Description} \\ \hline
\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where-based\\ Learner\end{tabular}} 
& threshold & 0.5 &[0.01,1]& The value to determine defective or not .\\ \cline{2-5} 
& infogain & 0.33 &[0.01,1]& The percentage of features to consider  for the best 
split to build CART tree\footnote{Since the Where-based learner will build two trees, the first 
one is for clustering and the second one is building prediction model. we explicitly call Where-
clustering tree and CART tree, respectively}. \\ \cline{2-5} 
& min\_sample\_size & 4& [1,10]& The minimum number of samples required to be a leaf for 
CART tree. \\ \cline{2-5} 
& min\_Size & 0.5 &[0.01,1]& \begin{tabular}[c]{@{}l@{}}The value to determine the minimum 
number of samples to be an internal node of the Where-clustering tree \\ based on  ${n\_samples}^ {min\_Size}$.
\end{tabular} \\ \cline{2-5} 
    & wriggle & 0.2 &[0.01, 1] & The threshold to determine which branch in  Where tree to be pruned\\ \cline{2-5}
& depthMin & 2 & [1,6]&The minimum depth of the tree below which no pruning for Where-
clustering tree. \\ \cline{2-5} 
& depthMax & 10 &[1,20]& The maximum depth of the Where-clustering tree. \\ \cline{2-5} 
& wherePrune & False &T/F& Whether or not to prune the Where-clustering tree. \\ \cline{2-5}
& treePrune & True &T/F& Whether or not to prune the classification tree built by CART. \\ \cline{2-5} 
\hline
\multirow{4}{*}{CART} & threshold & 0.5 &[0,1]& The value to determine defective or not. \\ \cline{2-5} 
& max\_feature & None &[0.01,1]& The number of features to consider when looking for the best 
split. \\ \cline{2-5}

& min\_sample\_split & 2 &[2,20]& The minimum number of samples required to split an 
internal node. \\ \cline{2-5} 
& min\_smaples\_leaf & 1 & [1,20]&The minimum number of samples required to be at a leaf 
node. \\ \cline{1-5}  
       \multirow{5}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}}  & threshold & 0.5 & [0.01,1] & The value to determine defective or not. \\ 
\cline{2-5} 
& max\_feature & None &[0.01,1]& The number of features to consider when looking for the best 
split. \\ \cline{2-5} 
& max\_leaf\_nodes & None &[1,50]& Grow trees with max\_leaf\_nodes in best-first fashion. \\ \cline{2-5} 
& min\_sample\_split & 2 &[2,20]& The minimum number of samples required to split an 
internal node. \\ \cline{2-5} 
& min\_smaples\_leaf & 1 &[1,20]&The minimum number of samples required to be at a leaf 
node. \\ \cline{2-5} 
&  n\_estimators & 100 & [50,150]&The number of trees in the forest.\\ \cline{2-5}
\hline

\end{tabular}
    \caption {List of parameters to be tuned in Where-based learner and CART in scikit-learn.}
\label{fig:parameters}
\end{figure*}

%%%%%%%%%%%%%%%% optimal parameters from tuning process%%%%%%%%%%%%%%%%%%%%%
%\begin{figure*}[t!]
%\scriptsize
%  \centering
%	\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
%	\hline
%	\begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default & 
%ant  & camel &ivy & jedit & log4j & lucene & poi & synapse & velocity & xalan & xerces \\ \hline
%	\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where-based\\ Learner\end{tabular}} 
%	& threshold & 0.5 & 0.16 & 0.87 &0.89 & 0.68 &0.58 &0.62&0.06&0.09&1&0.64 &0.02\\ \cline{2-14} 
%	& infogain & 0.33 & 0.33 & 0.49 &1&0.82 &0.12 &0.54&0.38&0.01&1&0.36&0.25\\ \cline{2-14} 
%	& min\_sample\_size & 4& 8 &1 &1&5&8&1&5&9&1&5&5\\ \cline{2-14} 
%	& min\_Size & 0.5& 1 & 0.67 & 0.99&1&0.63&1&0.95&0.59&1&0.88 &0.64\\ \cline{2-14} 
%	& wriggle &
%	& depthMin & 2 & 3 & 4 &1&1&2&1&1&5&1&1&3\\ \cline{2-14} 
%	& depthMax & 10 & 8 &14 &16&18&1&16&13&5&9&18&20\\ \cline{2-14} 
%	& wherePrune & False & True & True &False&False&False&True&True&False&True&False &True\\ \cline{2-14} 
%	& treePrune & True& False & True &True&True&False&False&True&False&False&False &False\\ 
%\hline
%	\multirow{4}{*}{CART} 
%	& threshold & 0.5 & 0.01 & 0.98 &0.94&0.67&0.47&1&0.01&0.12&0.9&0.57 &0.01\\ \cline{2-14} 
%	& max\_feature & None &0.01 & 1 &0.29&0.28&0.53&0.13&0.01&0.01&0.87&0.47 &0.01\\ \cline{2-14} 
%	%& max\_depth & None &27 & 46 &33&21&42&36&39&17&29&11&31\\ \cline{2-14} 
%	& min\_sample\_split & 2 &6 &2 &13&17&12&2&14&12&7&16 &13\\ \cline{2-14} 
%	& min\_smaples\_leaf & 1 &6 &3 &18&12&3&10&4&20&8&11&1\\ \hline  
%    \multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}}  
%    & threshold & 0.5 & 0.06 &0.88 &1&0.73&0.41&0.81&0.11&0.16&1&0.63&0.29\\ \cline{2-14} 
%	& max\_feature & None & 0.21 &0.98 &0.78&0.73&0.36&0.35&0.01&0.01&0.01&0.65 &0.89\\ \cline{2-14} 
%	& max\_leaf\_nodes & None & 31 &35 &41&40&23&12&26&41&46&49&35\\ \cline{2-14} 
%	& min\_sample\_split & 2 &12 &14 &2&5&8&11&1&16&1&9&20\\ \cline{2-14} 
%	& min\_smaples\_leaf & 1 &6 &15 &2&17&3&9&19&8&2&14&9\\ \cline{2-14} 
%	&  n\_estimators & 100 &111 &120 &89&68&64&84&107&100&79&113&50\\ \hline
%
%	\end{tabular}
%    \caption {Optimal parameters from tuning process with objetive of G measure over different data sets.}
%\label{fig:parameters}
%\end{figure*}

%%%%parameters for pd %%%%%%
\begin{figure*}[!t]

\renewcommand{\baselinestretch}{0.8}
\resizebox{\textwidth}{!}{
\scriptsize
\centering
  \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
    \hline
  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivyV0&jeditV0&jeditV1&jeditV2&log4jV0&luceneV0&poiV0&poiV1&synapseV0&velocityV0&xercesV0&xercesV1\\ 
 \hline
\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
& threshold& 0.5& 0.17& 0.17& 0.02& 0.04& 0.42& 0.7& 0.8& 0.25& 0.32& 0.13& 0.61& 0.77& 0.09& 0.02& 0.68& 0.17& 0.01\\ \cline{2-20}
& infoPrune& 0.33& 0.13& 0.06& 0.12& 0.35& 0.44& 0.26& 0.33& 0.81& 0.03& 0.32& 0.89& 0.05& 0.1& 0.97& 0.15& 0.24& 0.01\\ \cline{2-20}
& min\_sample\_size& 4& 5& 2& 4& 1& 7& 6& 9& 6& 9& 8& 1& 3& 3& 9& 5& 4& 2\\ \cline{2-20}
& min\_Size& 0.5& 0.49& 0.24& 0.41& 0.26& 0.12& 0.03& 0.26& 0.06& 0.19& 0.38& 0.02& 0.07& 0.2& 0.2& 0.32& 0.13& 0.86\\ \cline{2-20}
& wriggle& 0.2& 0.65& 0.19& 0.42& 0.37& 0.22& 0.56& 0.64& 0.26& 0.79& 0.97& 0.23& 0.52& 0.99& 0.78& 0.15& 0.58& 0.55\\ \cline{2-20}
& depthMin& 2& 4& 3& 2& 5& 5& 4& 3& 5& 4& 4& 2& 4& 2& 1& 4& 3& 1\\ \cline{2-20}
& depthMax& 10& 16& 7& 19& 11& 14& 16& 12& 12& 19& 17& 12& 13& 15& 13& 3& 17& 15\\ \cline{2-20}
& wherePrune& False& True& False& False& False& False& False& False& True& True& False& False& True& False& True& False& False& False\\ \cline{2-20}
& treePrune& True& True& True& True& False& False& False& False& False& True& True& False& False& True& False& False& True& False\\ \cline{2-20}
\hline
\multirow{4}{*}{CART}
& threshold& 0.5& 0.01& 0.13& 0.01& 0.01& 0.06& 0.34& 0.01& 0.15& 0.39& 0.01& 0.05& 0.06& 0.01& 0.01& 0.18& 0.06& 0.01\\ \cline{2-20}
& max\_feature& None& 0.01& 0.9& 0.01& 0.01& 0.45& 0.14& 0.52& 0.57& 0.76& 1& 0.68& 0.01& 0.33& 0.01& 0.73& 0.04& 0.01\\ \cline{2-20}
& min\_samples\_split& 2& 17& 20& 7& 18& 9& 11& 15& 16& 12& 11& 2& 6& 3& 13& 19& 13& 10\\ \cline{2-20}
& min\_samples\_leaf& 1& 11& 1& 9& 2& 19& 14& 6& 15& 4& 17& 19& 9& 12& 5& 4& 7& 13\\ \cline{2-20}
\hline
\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
& threshold& 0.5& 0.09& 0.01& 0.01& 0.01& 0.36& 0.49& 0.08& 0.01& 0.01& 0.01& 0.05& 0.01& 0.01& 0.01& 0.2& 0.15& 0.01\\ \cline{2-20}
& max\_feature& None& 0.01& 0.63& 0.01& 1& 0.19& 0.17& 0.01& 0.01& 0.95& 0.01& 0.65& 0.54& 0.01& 0.01& 0.45& 0.63& 0.2\\ \cline{2-20}
& max\_leaf\_nodes& None& 31& 43& 28& 29& 11& 48& 17& 25& 13& 25& 10& 31& 33& 47& 44& 14& 23\\ \cline{2-20}
& min\_samples\_split& 2& 2& 7& 13& 1& 9& 13& 1& 13& 6& 10& 4& 12& 19& 16& 17& 3& 13\\ \cline{2-20}
& min\_samples\_leaf& 1& 17& 18& 2& 20& 2& 18& 9& 6& 7& 11& 17& 19& 8& 17& 3& 13& 9\\ \cline{2-20}
& n\_estimators& 100& 76& 64& 62& 141& 91& 67& 57& 104& 70& 67& 56& 59& 97& 81& 140& 85& 92\\ \cline{2-20}
\hline  \end{tabular}
}
  \caption{Parameters tuned on different models over the objective of pd}
\end{figure*}

%%%%parameters for prec %%%%%%
\begin{figure*}[!ht]

\renewcommand{\baselinestretch}{0.8}
\resizebox{\textwidth}{!}{
\scriptsize
\centering
  \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
    \hline
  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivyV0&jeditV0&jeditV1&jeditV2&log4jV0&luceneV0&poiV0&poiV1&synapseV0&velocityV0&xercesV0&xercesV1\\ 
 \hline
\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
& threshold& 0.5& 0.53& 0.48& 0.41& 0.35& 0.88& 1& 1& 0.9& 0.96& 0.57& 1& 1& 0.56& 0.57& 0.8& 0.26& 0.65\\ \cline{2-20}
& infoPrune& 0.33& 0.68& 0.74& 0.31& 0.45& 0.78& 0.31& 0.53& 0.85& 0.04& 0.73& 0.54& 0.15& 1& 0.98& 0.23& 0.9& 0.19\\ \cline{2-20}
& min\_sample\_size& 4& 3& 6& 5& 2& 1& 5& 7& 1& 7& 5& 2& 8& 1& 1& 1& 2& 2\\ \cline{2-20}
& min\_Size& 0.5& 0.07& 0.23& 0.2& 0.21& 0.25& 0.54& 0.18& 0.36& 0.28& 0.51& 1.0& 0.33& 0.5& 0.84& 0.83& 0.04& 0.21\\ \cline{2-20}
& wriggle& 0.2& 0.91& 0.77& 0.58& 0.85& 0.17& 0.66& 0.33& 0.88& 0.13& 0.72& 0.18& 0.07& 0.43& 0.63& 0.74& 0.18& 0.75\\ \cline{2-20}
& depthMin& 2& 4& 2& 5& 2& 4& 2& 2& 2& 4& 2& 3& 4& 1& 5& 1& 2& 1\\ \cline{2-20}
& depthMax& 10& 10& 14& 6& 13& 7& 16& 15& 14& 13& 19& 16& 9& 16& 14& 11& 13& 15\\ \cline{2-20}
& wherePrune& False& True& False& True& True& True& True& True& True& True& True& True& True& True& True& False& True& False\\ \cline{2-20}
& treePrune& True& True& True& True& True& True& True& False& False& False& True& False& True& True& False& False& False& False\\ \cline{2-20}
\hline
\multirow{4}{*}{CART}
& threshold& 0.5& 0.76& 0.99& 0.86& 0.48& 1& 1& 1& 0.71& 0.62& 0.65& 1& 0.95& 0.64& 0.5& 1& 0.99& 1\\ \cline{2-20}
& max\_feature& None& 0.09& 0.13& 0.05& 0.01& 0.01& 0.47& 0.01& 0.1& 0.63& 0.62& 0.44& 0.27& 0.28& 0.04& 0.75& 0.96& 0.21\\ \cline{2-20}
& min\_samples\_split& 2& 4& 19& 9& 9& 17& 14& 14& 16& 14& 12& 17& 3& 10& 12& 20& 13& 6\\ \cline{2-20}
& min\_samples\_leaf& 1& 15& 17& 8& 7& 1& 20& 1& 9& 12& 15& 10& 13& 7& 10& 4& 7& 20\\ \cline{2-20}
\hline
\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
& threshold& 0.5& 0.92& 0.99& 0.71& 0.7& 1& 0.82& 1& 1& 1& 0.96& 0.73& 1& 0.76& 0.33& 1& 1& 0.98\\ \cline{2-20}
& max\_feature& None& 0.23& 0.13& 0.46& 0.69& 0.37& 0.56& 0.71& 0.01& 1& 0.01& 0.85& 0.48& 0.34& 0.02& 0.01& 0.08& 0.62\\ \cline{2-20}
& max\_leaf\_nodes& None& 12& 49& 23& 39& 10& 17& 20& 10& 10& 44& 37& 18& 35& 11& 31& 35& 28\\ \cline{2-20}
& min\_samples\_split& 2& 18& 8& 14& 1& 11& 3& 2& 1& 4& 14& 2& 1& 13& 8& 18& 2& 13\\ \cline{2-20}
& min\_samples\_leaf& 1& 11& 5& 11& 3& 2& 4& 20& 2& 2& 10& 3& 7& 7& 15& 6& 2& 9\\ \cline{2-20}
& n\_estimators& 100& 130& 146& 66& 96& 50& 50& 136& 84& 83& 129& 51& 150& 99& 58& 88& 85& 61\\ \cline{2-20}
\hline  \end{tabular}
}
  \caption{Parameters tuned on different models over the objective of prec}
\end{figure*}

%%%%parameters for F %%%%%%
\begin{figure*}[!ht]

\renewcommand{\baselinestretch}{0.8}
\resizebox{\textwidth}{!}{
\scriptsize
\centering
  \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
    \hline
  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivyV0&jeditV0&jeditV1&jeditV2&log4jV0&luceneV0&poiV0&poiV1&synapseV0&velocityV0&xercesV0&xercesV1\\ 
 \hline
\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
& threshold& 0.5& 0.12& 0.78& 0.3& 0.01& 0.78& 1& 0.99& 0.44& 0.72& 0.21& 0.41& 1& 0.04& 0.7& 0.36& 0.66& 0.42\\ \cline{2-20}
& infoPrune& 0.33& 0.58& 0.2& 0.41& 0.19& 0.82& 0.91& 0.35& 1& 0.85& 0.46& 0.24& 1.0& 0.85& 0.36& 0.48& 0.42& 0.82\\ \cline{2-20}
& min\_sample\_size& 4& 6& 1& 1& 6& 8& 6& 7& 5& 1& 5& 8& 2& 7& 5& 3& 1& 1\\ \cline{2-20}
& min\_Size& 0.5& 0.8& 0.75& 0.47& 0.01& 1& 0.64& 0.99& 0.43& 0.23& 0.47& 0.72& 1& 0.89& 0.69& 0.88& 0.38& 0.75\\ \cline{2-20}
& wriggle& 0.2& 0.21& 0.7& 0.83& 0.25& 0.55& 0.01& 0.63& 0.93& 0.43& 0.33& 0.52& 0.32& 0.72& 0.1& 0.43& 0.34& 0.1\\ \cline{2-20}
& depthMin& 2& 4& 5& 4& 3& 1& 6& 1& 4& 1& 1& 4& 1& 2& 2& 4& 5& 1\\ \cline{2-20}
& depthMax& 10& 16& 11& 5& 19& 8& 10& 14& 19& 5& 6& 6& 16& 3& 11& 5& 18& 12\\ \cline{2-20}
& wherePrune& False& True& True& True& False& True& False& False& True& True& True& False& True& True& False& True& False& True\\ \cline{2-20}
& treePrune& True& False& True& True& True& True& False& False& True& False& False& False& True& True& False& False& True& True\\ \cline{2-20}
\hline
\multirow{4}{*}{CART}
& threshold& 0.5& 0.01& 0.62& 0.13& 0.01& 1& 0.8& 0.7& 0.66& 0.72& 0.32& 0.09& 0.7& 0.01& 0.01& 0.91& 0.84& 0.01\\ \cline{2-20}
& max\_feature& None& 0.24& 0.88& 0.19& 0.01& 0.01& 0.8& 0.76& 0.28& 0.5& 0.22& 0.18& 0.01& 0.58& 0.01& 0.01& 0.3& 0.01\\ \cline{2-20}
& min\_samples\_split& 2& 19& 3& 13& 5& 2& 10& 8& 9& 11& 12& 7& 10& 20& 5& 4& 14& 11\\ \cline{2-20}
& min\_samples\_leaf& 1& 15& 18& 11& 13& 3& 13& 9& 10& 15& 8& 15& 15& 7& 10& 10& 4& 1\\ \cline{2-20}
\hline
\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
& threshold& 0.5& 0.01& 0.49& 0.14& 0.01& 1& 1& 1& 1& 1& 0.66& 0.53& 1& 0.01& 0.21& 1& 1& 0.01\\ \cline{2-20}
& max\_feature& None& 0.89& 0.21& 0.01& 0.04& 0.81& 0.45& 0.01& 0.49& 0.01& 0.01& 0.12& 0.81& 0.01& 0.07& 0.01& 0.62& 0.61\\ \cline{2-20}
& max\_leaf\_nodes& None& 21& 16& 49& 10& 26& 32& 39& 22& 10& 42& 24& 43& 38& 10& 10& 10& 20\\ \cline{2-20}
& min\_samples\_split& 2& 11& 9& 19& 15& 6& 14& 6& 3& 4& 10& 18& 2& 8& 7& 10& 10& 16\\ \cline{2-20}
& min\_samples\_leaf& 1& 6& 11& 13& 7& 16& 4& 2& 18& 2& 6& 19& 2& 9& 4& 17& 2& 5\\ \cline{2-20}
& n\_estimators& 100& 88& 99& 124& 148& 56& 101& 116& 55& 122& 112& 75& 55& 92& 129& 58& 107& 121\\ \cline{2-20}
\hline  \end{tabular}
}
  \caption{Parameters tuned on different models over the objective of F}
\end{figure*}

%%%%%%%%%%%%%%%% defectives and non-defectives for each datasets%%%%%%%%%%%%%%%%%%%%%

%\begin{figure*}[!th]
%  \scriptsize
%  \centering
%	\begin{tabular}{|l|l|l|}
%	\hline
%	\multicolumn{1}{|c|}{Data Set} & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}} Feature Selections\\ with  Default Parameters\end{tabular}} & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Feature Selection\\ with Tuning Parameters\end{tabular}} \\ \hline
%	  ant  & mfa, lcom3, cam, ic, dam   & wmc, lcom3, cam, dam, npm, rfc  \\ \hline
%	camel & cam, wmc, dit, mfa, rfc, loc & rfc, cam, loc, wmc, dam, dit, mfa, lcom3, npm\\ \hline
%	ivy & cam, dit, dam, ic, lcom3& cam, dam, mfa\\ \hline
%	jedit& mfa, dam, cam, dit, cbm, ic& mfa, loc, dit, dam, cam, wmc  \\ \hline
%	log4j & lcom3, mfa, loc, ic, dit& mfa, wmc  \\ \hline
%	lucene & mfa, lcom3, cam, dam, ic& wmc, lcom3, avg\_cc, rfc, ce, mfa, dam, npm, cam \\ \hline
%	poi & mfa, dam, amc, lcom3, cbm, loc& loc, lcom3, cam, amc, dam                                                     \\ \hline
%	synapse & dam, loc, mfa, cam & loc  \\ \hline
%	velocity& dit, dam, lcom3, ic, mfa& mfa, cam, avg\_cc, loc, lcom3, cbo, dam, ic, rfc, lcom \\ \hline
%	xalan  & mfa, cam, wmc, lcom3, rfc, dit & mfa, rfc, loc, dam, lcom3, wmc, npm \\ \hline
%	xerces & cam, wmc, mfa, rfc, amc, loc& mfa, loc, cam, amc, avg\_cc\\ \hline
%	\end{tabular}
%	\caption{Features selection before and after tuning over objective of G values }
%\end{figure*}

%%%%%%%%%%%%%%%% feature selection over pd%%%%%%%%%%%%%%%%%%%%%

\setlength{\tabcolsep}{3pt}
\renewcommand\arraystretch{1.2}

%%%%%%%%%%%%%% pd bars%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure*}
\renewcommand{\baselinestretch}{0.8}
\scriptsize
\begin{minipage}{0.81\linewidth}
\begin{tabular}{r@{~}|r@{~}l@{~}|r@{~}l@{~}|r@{~}l|r@{~}@{~}l|r@{~}l@{~}|r@{~}l@{~}|r@{~}l}
  \multicolumn{1}{c|}{~}&\multicolumn{11}{c}{median(pd) } \\
  Data set   &   \multicolumn{2}{c}{Naive\_Where}         &   \multicolumn{2}{c}{Tuned\_Where}         &   \multicolumn{2}{c}{Naive\_CART}         &   \multicolumn{2}{c}{Tuned\_CART}    &   \multicolumn{2}{c}{Naive\_RanFst}  &   \multicolumn{2}{c}{Tuned\_RanFst}\\\hline
\multicolumn{1}{c}{~}\\
antV0 & 53 & {\rone} & 100 & {\rfour} & 38 &         & 100 & {\rfour} & 78 & {\rthree} & 97 & {\rfour}\\
antV1 & 7 &         & 100 & {\rfour} & 39 & {\rone} & 100 & {\rfour} & 95 & {\rfour} & 100 & {\rfour}\\

>>>>

The psuedocode for differential evolution is shown in Algorithm~\ref{alg:DE}.
Note that, as we describe the algorithm,
  any superscript number denotes a line in that algorithm.

@@

The premise of this algorithm is that the best way to mutate existing tunings
is to {\em Extrapolate}$^{29}$
between current solutions.  Three solutions $a,b,c$ are selected at random.
For each tuning parameter $i$, at some probability {\em cr}, we replace
the old tuning $x_i$ with $y_i$ found as follows:
\bi
\item (For numerics) $y_i = a_i+f \times (b_i - c_i)$   where $f$ is a parameter
controlling the cross-over amount.  The {\em trim} function$^{39}$ limits the new
value to the legal range min..max of that parameter.
\item (For booleans) $y_i= \neg x_i$ (see line 37).
\ei
The main loop of DE$^7$ runs over the {\em Population}, replacing old items
with new {\em Candidate}s (if the new candidate is better than the old item).
This means that, as the loop progresses, the {\em Population} is full of increasiningly
more valuable solutions. This, in turn, also improves  the candidates (which are generated
from the {\em Population}.

@@

\section{Experimental Design}

The following experimental aims to compare the performance of three learners, tuned and untuned, on 17
sets of data.

@@

An important principle in data mining is not to test on the data used
in training.  There are many ways to design a experiment that satisfies this principle.
Some of those methods have certain drawbacks:
\bi
\item  Leave-one-out is too slow for large data sets;
\item Cross-validation can mix up older and newer data sets so it may well be that
data from the {\em future} is used to test on {\em past data}.
\ei
To avoid these problems, we used an incremental learning approach. The following
experiment ensures that the training data was created at some time before the test
data.

For this experiment, we looked for data sets that had at least three  
releases in PROMISE. Note that the following ensures that all treatments 
get assessed on the same test  set.
\bi 
\item The {\em first} release was used for some  {\em training}, to collect a baseline
   using an untuned learner.
   \item
   The {\em first} release was also used  on line 24 of Algorithm~\ref{alg:DE} to
   build some model using some the tunings found in some {\em Candidate}.
   \item The {\em second} release was used on 25 of Algorithm~\ref{alg:DE} to 
   test the model found on line 24.
   \item Finally the {\em third} release was used to gather the performance statistics
   reported below from (a)~the model generated by the untuned learner or (b)~the
   best model found by differential evolution.
   \ei
Some data sets have more than three releases and, for those data, we could run more
 than one experiment. For example, {\em ant} has five versions in PROMISE so
 we ran three experiments called V0,V1,V2:
 \bi
 \item AntV0: first,second,third = versions 1,2,3
 \item AntV1: first,second,third = versions 2,3,4
 \item AntV2: first,second,third = versions 3,4,5
 \ei 
These data sets are displayed in \fig{data1} and \fig{data2}.

\subsection{Optimization Goals}

Recall from Algorithm~! that we call differential evolution one time for each
goal we are trying to optimize. This section lists those optimization goals.

Let $\{A,B,C,D\}$ denote the
true negatives, 
false negatives, 
false positives, and 
true positives
(respectively) found by a binary detector. 
Certain standard measures can be computed from
$A,B,C,D$: 
\[
\begin{array}{ll}
pd=recall=&\frac{D}{B+D}\\
pf=&\frac{C}{A+C}\\
pf'=& 1 - pf\\
prec=precision=&\frac{D}{D+C}\\ 
 g = & \frac{2*pd*pf'}{pd + pf'}
\end{array}
\]
All the above vary from zero to one. For $pf$, the {\em better} scores and {\em smaller}.
For all other scores, the {\em better} scores are {\em larger}.

The following results make no assumption that (e.g.) minimizing false alarms are 
more important that maximizing recall or precision. That determination 
should be make with respect to current business conditions:
\bi
\item
For safety critical applications, low false alarm rates are irrelevant since the cost
of overlooking any critical might outweigh the inconvenience of having to inspect a few more
modules. 
\item
On the other hand, when rushing a product to market before a competing product is released, there is a business case to 
avoid the extra rework associated with false alarms.  In that business context, 
managers might be willing to lower the recall somewhat in order to minimize the false alarms.
\ei
What the falling results do show is that once the optimization goal changes, so does everything
else. Hence, it is important not to overstate  empirical results from software analytics.
Rather, those results need to be expressed {\em along with} the context within which they are
relevant.

\section{Experimental Results}

The introduction of this article made several claims about tuning defect predictor
that use static code attributes. This section presents
our results in order of those claims:
\be
\item Such tuning was easy (see \tion{easy});
\item Such tuning is fast (see \tion{fast});
\item Such tuning is can dramatically change the performance scores of a predictor;
e.g. one result where precision changes from 2\% to 98\% (see \tion{precision});
\item Tuning changes conclusions about what factors are most important (see \tion{import});
\item Tuning changes conclusions about what learners are better than others (see \tion{rank};)
\ee

\subsection{Tuning is Easy}

All the following results are generated with a a very simple optimizer
(differential evolution). Further, our DE  is actually much simpler
than a standard implementation. Recall from Algorithm~1 that
DE explores a {\em Population} of size {\em np=10}. This is a very small population size:
the standard recommendation is to set {\em np} to be ten times larger than the number
of attributes being optimized~\cite{stron97}

The results of this paper are presented

@@
